XXX in a Tracing JIT Compiler for Efficient Dynamic Languages

### 2011-03-25 talk/icooolps2011/paper.tex
change diagram to make it fit into one column to save space
add a missing return, change_method -> write_method
remove duplication

In this paper we present two of these hints that are extensively used in the
PyPy project to improve the performance of its Python interpreter.
 The

PyPy's hints go even further than SPUR's in that they provide the interpreter
author with a flexible toolset to make her implementation extremely efficient.
In this paper we present the two most prominent ones and show how classical
implementation techniques of dynamic languages can be expressed with them. These
hints are used to control how the optimizer of the tracing JIT can improve the
traces of the object model. More specifically, these hints influence the
constant folding optimization. The first hint make it possible to turn arbitrary
variables in the trace into constants. The second hint allows the definition of
additional foldable operations.

@@

\begin{figure*}
\includegraphics[scale=0.5]{figures/trace-levels}
\caption{The levels involved in tracing}
\label{fig:trace-levels}
\end{figure*}

@@

The index \texttt{0} that is used to read out of the \texttt{storage} array is the result
of the constant-folded \texttt{getindex} call.
The constants \texttt{41} and \texttt{17} are the results of the folding of the
\texttt{\_find\_method`} calls. This final trace is now very good. It no longer performs any
dictionary lookups. Instead it contains several guards. The first guard
checks that the map is still the same. This guard will fail if the same
code is executed with an instance that has another layout. The second guard
checks that the class of \texttt{inst} is still the same. It will fail if the trace is
executed with an instance of another class. The third guard checks that the
class did not change since the trace was produced. It will fail if somebody
calls the \texttt{change\_method} method on the class.

>>>>

In this paper we present two of these hints that are extensively used in the
PyPy project to improve the performance of its Python interpreter. These
hints are used to control how the optimizer of the tracing JIT can improve the
traces of the object model. More specifically, these hints influence the
constant folding optimization. The first hint make it possible to turn arbitrary
variables in the trace into constants. The second hint allows the definition of
additional foldable operations.

@@

\begin{figure}
\includegraphics[scale=0.5]{figures/trace-levels}
\caption{The levels involved in tracing}
\label{fig:trace-levels}
\end{figure}

@@

The index \texttt{0} that is used to read out of the \texttt{storage} array is the result
of the constant-folded \texttt{getindex} call.
The constants \texttt{41} and \texttt{17} are the results of the folding of the
\texttt{\_find\_method`} calls. This final trace is now very good. It no longer performs any
dictionary lookups. Instead it contains several guards. The first guard
checks that the map is still the same. This guard will fail if the same
code is executed with an instance that has another layout. The second guard
checks that the class of \texttt{inst} is still the same. It will fail if the trace is
executed with an instance of another class. The third guard checks that the
class did not change since the trace was produced. It will fail if somebody
calls the \texttt{write\_method} method on the class.
